---
title: "Chicago Bulls FG% Data"
author: "Aryan Kancherla"
execute: 
  echo: false
  warning: false
---

The Chicago Bulls had a great season this year, qualifying for the NBA Play-in tournament and eliminating the Toronto Raptors. The following data was pulled from FantasyPros, a website that provides fantasy sports data & content. Then, the data was filtered to look at the statistics of all the Chicago Bulls players. Finally, I created a Bayesian Prediction Model estimating the Field Goal Percentage of the Chicago Bulls Team. In the 2022-2023 NBA Season, the Chicago Bulls' estimated average field goal percentage was 49.2%, represented by the dotted black line on the histogram. 

```{r}
#| message: false
library(tidyverse)
library(rstanarm)
library(readr)
library(ggplot2)
```

```{r}
#| message: false
#| warning: false
NBA_Data <- read_csv("data/NBA-2022-2023-Data.csv", col_types = cols(
  Player = col_character(),
  Team = col_character(),
  Positions = col_character()
  )
) |> 
  filter(Team == "CHI") |>
    filter(`GP` > 10)

```

```{r}
#| message: false

fit_obj <- stan_glm(data = NBA_Data, 
                    formula = `FG%` ~ 1, 
                    family = gaussian, 
                    refresh = 0,
                    seed = 9)

newobs <- tibble(.rows = 1)

pe <- posterior_epred(object = fit_obj, newdata = newobs) |> 
  as_tibble()
```

```{r}
pe |> 
  ggplot(aes(x = `1`)) +
    geom_histogram(aes(y = after_stat(count/sum(count))), fill = "red", color = "black", bins = 100) +
      geom_vline(xintercept = median(pe$`1`), linetype = "dotted", lwd = 1.5) + 
       labs(title = "Estimated Team FG% of the Chicago Bulls",
         subtitle = "The values in this graph are estimated",
         x = "Estimated FG%",
         y = "Probability",
         caption = "Source: FantasyPros"
         ) +
  scale_x_continuous(labels = scales::number_format(accuracy = 0.01))+
          scale_y_continuous(labels = scales::percent_format()) +
            theme_classic()
```
