---
title: "Chicago Bulls Field Goal Percentage Prediction"
author: "Aryan Kancherla"
execute: 
  echo: false
  warning: false
---

```{r}
#| message: false
library(tidyverse)
library(rstanarm)
library(ggplot2)
```

```{r}
#| message: false
#| warning: false

# Importing the csv file and changing the column types of the "Players", "Team", and "Position" columns to characters

NBA_Data_1 <- read_csv("data/NBA-2022-2023-Data.csv", col_types = cols(
  Player = col_character(),
  Team = col_character(),
  Positions = col_character()
  ) 
  
  #Filtered the data, analyzing Chicago Bull players who have played more than 30 games. Then, selecting the "Player" and "FG%" columns from the data
  
) |>
  filter(Team == "CHI") |>
    filter(`GP` > 30) |>
      select(`Player`, `FG%`)

#Added Jevon Carter to the data, as he was recently signed by the Chicago Bulls this offseason


new_row <- tibble(Player = "Jevon Carter", `FG%` = 0.423)
NBA_Data <- add_row(NBA_Data_1, .before = 1, !!!new_row)


```

```{r}
#| message: false

# Created the fitted model, using a one parameter model


fit_obj <- stan_glm(data = NBA_Data, 
                    formula = `FG%` ~ 1, 
                    family = gaussian, 
                    refresh = 0,
                    seed = 9)

newobs <- tibble(.rows = 1)

pe <- posterior_epred(object = fit_obj, newdata = newobs) |> 
  as_tibble()

# pe is now a tibble which holds all the predicted values of the Chicago Bulls' Field Goal Percentage

```

```{r}
pe |> 
  ggplot(aes(x = `1`)) +
    geom_histogram(aes(y = after_stat(count/sum(count))), fill = "red", color = "black", bins = 100) +
  
  #Used geom_vline (the black dotted line on the histogram) to display the predicted FG% of the Chicago Bulls for the 2023-2024 NBA Season 
  
      # the xintercept value is the mean of all the predicted values, which is the predicted FG% of the Bulls
  
      geom_vline(xintercept = mean(pe$`1`), linetype = "dotted", lwd = 1.5) +
  
    # Used the annotate() function to create a label for the vline, setting the x-value of the label at the mean of the data.

  
      annotate("text", x = mean(pe$`1`), y= 0.015, label = "Mean: 0.4872186", angle = 0, color = "white") +
  
       labs(title = "The Chicago Bulls Predicted Field Goal % for the 2023-2024 NBA Season",
         subtitle = "It is likely that the Field Goal Percentage will be 48.7% next season",
         x = "Predicted FG%",
         y = "Probability",
         caption = "Source: FantasyPros"
         ) +
  
  # Used scale_x_continuous to format the x-axis ticks
  # accuracy() is used to accurately create the x-axis ticks
  
  scale_x_continuous(labels = scales::number_format(accuracy = 0.01)) +
  
  
    # used the theme() function to hide the y-axis, as it is not needed for this graph

            theme_classic() + 
              theme(axis.title.y = element_blank(),
               axis.text.y = element_blank(),
               axis.ticks.y = element_blank())
```

## Plot Summary

The Chicago Bulls had a great season this year, qualifying for the NBA Play-In Tournament and eliminating the Toronto Raptors. The following data was pulled from FantasyPros, a website that provides fantasy sports data & content. Then, the data was filtered to look at the statistics of all the Chicago Bulls players. Finally, I created a Bayesian Prediction Model estimating the Field Goal Percentage of the Chicago Bulls Team. For the 2023-2024 NBA Season, the Chicago Bulls' predicted average field goal percentage is [48.7%]{.underline}, represented by the dotted black line on the histogram.
