---
title: "players"
editor: visual
execute:
  echo: false
---

```{r}
#| message: false
library(tidyverse)
library(rstanarm)
library(readr)
library(ggplot2)
library(plotly)
```

The interactive scatterplot below shows the individual Field Goal Percentages (FG%) of Chicago Bulls players who have played at least 1000 minutes during the 2022-2023 NBA Season. 

```{r}
#| message: false
#| warning: false
NBA_Data <- read_csv("data/NBA-2022-2023-Data.csv", col_types = cols(
  Player = col_character(),
  Team = col_character(),
  Positions = col_character()
  )
) |>
  filter(Team == "CHI") |>
    arrange(desc(MIN)) |>
      filter(MIN >= 1000)


```

```{r}
BullsPlayerPlot <- NBA_Data |>
    ggplot(
      aes(
        x = Player, 
        y = `FG%`,
        fill = "red",
        color = "black"
        )) +
      geom_point(stat = "identity") + 
          labs(
            title = "Individual Player Field Goal Percentages",
            subtitle = "All the players on this graph have played at least 60 games during the 2022-2023 season ",
            x = "Players",
            y = "Field Goal Percentage",
            caption = "Source: FantasyPros"
          ) + theme_classic() + 
          theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplotly(BullsPlayerPlot)
```


## Plot Summary

The scatterplot above shows that out of all the Chicago Bulls players that had played at least 1000 minutes, Nikola Vucevic had the highest FG%. I believe this result to be accurate as Nikola Vucevic has played a significant amount of minutes (2746 to be exact) during the 2022-2023 NBA Season. Also, Vucevic's position (Center) requires him to take frequent layups, dunks, and mid-range shots, validating his FG%. 

