---
title: "players"
editor: visual
execute:
  echo: false
---

```{r}
#| message: false
library(tidyverse)
library(rstanarm)
library(ggplot2)
library(plotly)
```

The interactive scatterplot below shows the individual Field Goal Percentages (FG%) of Chicago Bulls players who have played at least 1000 minutes during the 2022-2023 NBA Season. 

```{r}
#| message: false
#| warning: false
NBA_Data_1 <- read_csv("data/NBA-2022-2023-Data.csv", col_types = cols(
  Player = col_character(),
  Team = col_character(),
  Positions = col_character()
  )
) |>
  filter(Team == "CHI") |>
    arrange(desc(MIN))|>
      filter(MIN >= 1000) |>
        select(Player, `FG%`, Positions)

new_row <- tibble(Player = "JeVon Carter", `FG%` = 0.423, Positions = "PG,SG")
NBA_Data <- add_row(NBA_Data_1, .before = 1, !!!new_row)



```

```{r}
BullsPlayerPlot <- NBA_Data |>
    ggplot(
      aes(
        x = Player, 
        y = `FG%`,
        fill = Player,
        text = paste("Position: ", Positions, "\n", "FG%: ", (`FG%` * 100),  sep = "")
        )) +
      geom_point(stat = "identity") + 
          labs(
            x = "Players",
            y = "Field Goal Percentage",
            caption = "Source: FantasyPros"
          ) + theme_classic() + 
          theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "none")

ggplotly(BullsPlayerPlot, tooltip = "text") |>
  layout(title = list(text = paste('Individual Player Field Goal Percentages for the 2022-2023 NBA Season', '<br>', '<sup>', 'Vucevic had the highest field goal percentage(52%)', '</sup>')))
```


## Plot Summary

The scatterplot above shows that out of all the Chicago Bulls players that had played at least 1000 minutes, Nikola Vucevic had the highest FG%. I believe this result to be accurate as Nikola Vucevic has played a significant amount of minutes (2746 to be exact) during the 2022-2023 NBA Season. Also, Vucevic's position (Center) requires him to take frequent layups, dunks, and mid-range shots, validating his FG%. 

